---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

load data in unzipped activity.csv file
```{r}
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

Calculate total steps per day ignoring intervals with missing data (na) and plot histogram
```{r}
s1 <- split(data, data$date)
Steps_Per_Day <- sapply(s1, function(x) sum(x[, "steps"], na.rm=T))
hist(Steps_Per_Day)
```

Calculate and display mean total steps per day
```{r}
print(mean(Steps_Per_Day))
```

Calculate and display median total steps per day
```{r}
print(median(Steps_Per_Day))
```

## What is the average daily activity pattern?
Calculate and plot Mean_Steps_Per_Interval
```{r}
s2 <- split(data, data$interval)
Mean_Steps_Per_Interval <- sapply(s2, function(x) mean(x[, "steps"], na.rm=T))
plot(Mean_Steps_Per_Interval, xlab = "Interval # (Each interval is 5 minutes long)")
```

Determine the interval which, on average across all days in the dataset, contains the maximal number of steps. Display the interval and then the average number of steps in that interval.
```{r}
sorted <- sort(Mean_Steps_Per_Interval, decreasing=T)
print(sorted[1])
```
The maximum mean steps per interval occurred in interval 835 and was 206.1698 steps.

## Imputing missing values

Determine and display the total number of intervals where data on steps is missing
```{r}
y <- sum(is.na(data$steps))
print(y)
```




## Are there differences in activity patterns between weekdays and weekends?
